\Title

### 2016-08-18 manuscript/manuscript.tex
Main advantages of our method in the conclusion
Fixes #30

>>>>

There are two main advantages of the proposed method over previous works.
First, unlike the Parker-Oldenburg method \citep{oldenburg1974} or methods
using rectangular prisms, our inversion method does not require the data to be
projected onto a plane.
Second, the Parker-Oldenburg method and methods derived from \citet{bott1960}
\citep[e.g., ][]{silva2014,santos2015} cannot apply the
traditional methodology for constraining inverse problems
described in \citet{silva2001b}.
Our method has no such restriction because we use the formalism of traditional
Tikhonov inversion.
However, the proposed method is not without limitations.
It requires data on a regular grid and restricts the
model to be a regular mesh tied to the data grid.
There is also the limitation that, like \citet{bott1960},
our method only works for gravity disturbances and not the gravity gradients.
